Source: kaggle

Context and Content
A company which is active in Big Data and Data Science wants to hire data scientists among people who successfully pass some courses which conduct by the company. Many people signup for their training. Company wants to know which of these candidates really want to work for the company after training or are looking for a new employment because it helps to reduce the cost and time as well as the quality of training or planning the courses and categorization of candidates. Information related to demographics, education, experience are in hands from candidates signup and enrollment.

The whole data is divided in two groups: train and test. 

Note:

The dataset is imbalanced.
Most features are categorical (Nominal, Ordinal, Binary), some with high cardinality.
Missing imputation can be a part of your pipeline as well.
Features

enrollee_id : Unique ID for candidate

city: City code

city_ development _index : Developement index of the city (scaled)

gender: Gender of candidate

relevent_experience: Relevant experience of candidate

enrolled_university: Type of University course enrolled if any

education_level: Education level of candidate

major_discipline :Education major discipline of candidate

experience: Candidate total experience in years

company_size: No of employees in current employer's company

company_type : Type of current employer

lastnewjob: Difference in years between previous job and current job

training_hours: training hours completed

target: 0 – Not looking for job change, 1 – Looking for a job change
